%% thesis.tex 2014/04/11
%
% Based on sample files of unknown authorship.
%
% The Current Maintainer of this work is Paul Vojta.

\documentclass{ucbthesis}
\usepackage{amsmath, amssymb}
\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\usepackage{bm}
\usepackage{natbib}
\usepackage{hyperref}
\usepackage{booktabs}
\usepackage{multicol}
\usepackage{multirow}
\usepackage{aas_macros}
\usepackage{rotating}
\usepackage{longtable}
% \usepackage[natbib=true, backend=bibtex, style=authoryear]{biblatex}
% \bibliography{references}

\newcommand{\lcdm}{$\texrm{\Lambda}$CDM}
\newcommand{\angstrom}{\mbox{\normalfont\AA}}
\newcommand{\stoe}{\texttt{spec2embed}}
\newcommand{\etos}{\texttt{embed2spec}}
\newcommand\ion[2]{#1$\;${\scshape{#2}}}
\newcommand{\siliconii}{\ion{Si}{II} \texorpdfstring{$\lambda$}{}6355}
\newcommand{\CaIIHK}{\ion{Ca}{II} H\&K}
\newcommand{\SiIIred}{\ion{Si}{II} $\lambda$6355}
\newcommand{\SiIIblue}{\ion{Si}{II} $\lambda$5972}
\newcommand{\sn}{SN~Ia}
\newcommand{\sne}{SNe~Ia}
\newcommand{\snf}{SNfactory}

\defcitealias{boone_twins_2020a}{B20a}
\defcitealias{boone_twins_2020b}{B20b}

% To compile this file, run "latex thesis", then "biber thesis"
% (or "bibtex thesis", if the output from latex asks for that instead),
% and then "latex thesis" (without the quotes in each case).

% Double spacing, if you want it.  Do not use for the final copy.
% \def\dsp{\def\baselinestretch{2.0}\large\normalsize}
% \dsp

% If the Grad. Division insists that the first paragraph of a section
% be indented (like the others), then include this line:
% \usepackage{indentfirst}

\begin{document}

% Declarations for Front Matter

\title{Using Empirical Models of Type Ia Supernovae to Prepare for Next-Generation Cosmological Measurements}
\author{Samantha Mary Dixon}
\degreesemester{Fall}
\degreeyear{2020}
\degree{Doctor of Philosophy}
\chair{Professor Saul Perlmutter}
\othermembers{Professor Daniel Kasen \\
Professor Fernando P\'{e}rez}
\numberofmembers{3}
% Previous degrees are no longer to be listed on the title page.
% \prevdegrees{B.A. (University of Northern South Dakota at Hoople) 1978 \\
%   M.S. (Ed's School of Quantum Mechanics and Muffler Repair) 1989}
\field{Physics}
% Designated Emphasis -- this is optional, and rare
% \emphasis{Colloidal Telemetry}
% This is optional, and rare
% \jointinstitution{University of Western Maryland}
% This is optional
\campus{Berkeley}

% For a masters thesis, replace the above \documentclass line with
% \documentclass[masters]{ucbthesis}
% This affects the title and approval pages, which by default calls this
% document a "dissertation", not a "thesis".

\maketitle
% Delete (or comment out) the \approvalpage line for the final version.
% \approvalpage
\copyrightpage

\include{abstract}

\begin{frontmatter}

% \begin{dedication}
% \null\vfil
% \begin{center}
% \end{center}
% \vfil\null
% \end{dedication}

% You can delete the \clearpage lines if you don't want these to start on
% separate pages.

\tableofcontents
\clearpage
\listoffigures
\clearpage
\listoftables
\begin{acknowledgements}
Writing this dissertation would not have been possible without the advice, encouragement, and kindness of my advisors, colleagues, family, and friends.

I first want to thank my advisor, Saul Perlmutter, for being such an enthusiastic and supportive mentor. Working with Saul has shaped me as a scientist, and I'm deeply grateful to have had his guidance while also having the freedom to pursue the ideas that interested me the most. Greg Aldering has also been a valued mentor; I have him to thank for most of what I know about observing and for pointing me in the right directions early on in my research career. I also want to thank my undergraduate thesis advisor, Paolo Privitera, for encouraging me to go to graduate school in the first place, and for pushing me to aim high and apply to Berkeley. I'm only writing this now because of that push. Thank you to my qualification exam and dissertation committee members, Bill Holzapfel, Dan Kasen, and Fernando P\'{e}rez, who gave me plenty of advice to guide my work and to better this document. 

Many thanks are due to all of the officemates I've had over the years, including Kyle Boone, Kara Ponder, Ravi Gupta, Clare Saunders, Aleksander Cikota, and Brian Hayden. Each of them has taught me an immeasurable amount about physics, astronomy, statistics, computing, writing, and life that made all of the work here possible. I already miss all of our lunch-time conversations in the LBL cafeteria. Ben Rose, David Rubin, and Rebekah Hounsell have been wonderful colleagues over the years. I'm grateful for all of the Slack chats, paper editing sessions, code reviews, and answers to my silly questions.

Jeffrey Epstein and Jennet Dickinson have been my greatest friends throughout grad school, from staying up late first year to cram for prelims to getting up early 6 years later to make dissertation edits. I'm thankful to have had the world's best homework helpers, brunch partners, breakup text proofreaders, and close confidants on my side all these years. I also want to thank Jessica Avva for helping me to prove that being obsessed with the Bachelor doesn't have to be antithetical to becoming a great scientist, and for being such a strong and supportive friend. I could not have finished writing all this up without the tireless support (and homecooked meals) of Michael Mangus; thank you for always reminding me how capable I am. 

Finally, I want to thank my parents for their unconditional love and support, and for trying their best to understand even when they don't have any clue what I'm talking about. Thank you for instilling in me the love of learning that brought me to Chicago and to Berkeley, and for raising me to have the confidence to see it all through.
\end{acknowledgements}

\end{frontmatter}

\pagestyle{headings}

\include{intro}
\include{cte}
\include{si_feat_pca}
\include{snemo_kde}
\include{nonsim_reg_bias}
\include{nn_twins}
\include{conclusion}

\bibliographystyle{aasjournal}
\bibliography{references}

\appendix
\include{appendix_si_feat_pca}
\include{appendix_si_measurements}
\include{appendix_kde}
\include{appendix_spec_feat}
\include{appendix_reg_bias}
\end{document}